SMT-Boosted Security Types and Correctness for Low-Level MPC

### 2025-11-24 toplas26/metalang.tex
checkpoint

The $\metaprot$ language \cite{skalka-near-ppdp24} includes structured
data and function definitions for defining composable protocol
elements at a higher level of abstraction than $\minicat$.  The
$\metaprot$ language is a \emph{metalanguage} aka metaprogramming
language, where an $\fedprot$ protocol is the result of
computation. In addition to these declarative benefits of $\metaprot$,
component definitions support compositional verification of larger
protocols. This includes an automated verification of algebraic
program properties expressed as Hoare logic assertions that we
introduce in this Section. Furthermore, we can compositionally verify
confidentiality and integrity properties expressed as types, as we
will show in Section \ref{section-sharety}. We present and discuss
extended examples of $\metaprot$ programs in Section
\ref{section-examples}.

@@

The syntax of $\metaprot$ is defined in Figure
\ref{fig-metaprotsyntax}.  It includes a syntax of values $\mv$ that
include client ids $\cid$, identifier strings $w$, expressions $\be$
in field $\mathbb{F}_p$, record values, and $\minicat$ variables
$x$. $\metaprot$ expression forms allow dynamic construction of these
values. Note in particular that $\concat$ is string concatentation.
$\metaprot$ \emph{instructions} allow dynamic
construction of $\minicat$ protocols $\prog$ that incorporate expression
evaluation. The syntax also supports definitions of functions that
compute values $\mv$ and, as a distinct form, functions that compute
protocols $\prog$.  The latter requires type annotations on arguments
which are restricted to being either strings, client ids, or
records-- we use this type information to support Hoare logic
automation as we discuss below in Section \ref{section-metahtrip}.

Formally, we consider a complete metaprogram to include
both a codebase and a ``main'' program that uses the codebase.
We disallow recursion, mainly to guarantee decidability
of type dependence (Section \ref{section-metalangty}).
\begin{definition}
A \emph{codebase} $\codebase$ is a list of function 
declarations. We write $ \codebase(f) = y_1,\ldots,y_n,\ e$
if $f(y_1,\ldots,y_n) \{ e \} \in \codebase$, and we
write  $ \codebase(f) = y_1 : \tau_1, \ldots, y_n : \tau_n, \instr$
if $f(y_1 : \tau_1, \ldots, y_n : \tau_n) \{ \instr \} \in \codebase$.
%A \emph{metaprogram}, aka \emph{metaprotocol}  is a pair of a 
%codebase and expression $\codebase, e$. We may omit
%$\codebase$ if it is clear from context.  
\end{definition}

@@

Note that we do not include an evaluation
rule for the form $\eqcast{\mx{e}{e}}{e}$ which is a type
annotation that we assume is erased from programs prior to
evaluation. We defer discussion of this form to Section
\ref{section-sharety}

@@

$\metaprot$ instruction functions can optionally be annotated with
pre and postconditions. To model this in our theory we posit
functions $\precond$  and $\postcond$ 
that specify conditions for instruction functions $f \in \dom(\codebase)$.
Note that $\precond(f)$ or $\precond(f)$ may be undefined if no annotation
is given for $f$. In actual code, we write pre and postconditions directly before and
after functions to define them. Here is a simple example function $\ttt{bar}$
with. Note that the pre and postconditions are abstract with respect to the
input string $\ttt{x}$, and that string concatenation  
can be used in pre and postcondition constraints:
\begin{verbatimtab}
precondition: ( m[x++"foo"]@1 == 3 )
bar(x:string){ m[x++"bar"]@2 := (m[x++"foo"] + m[x++"baz"])@1 }
postcondition: ( [m[z++"bar"]@2 == m[x++"baz"]@1 + 3 )
\end{verbatimtab}
Since expressions can occur in $\metaprot$ constraints, they are not
SMT constraints, but abstractions of constraints parameterized by
the formal parameters of the function they annotate. We denote these
\emph{abstract constraints} as $\eqs$ with the syntax given
in Figure \ref{fig-peq}. When the function is applied, the pre and postconditions
are instantiated as SMT constraints, via evaluating the expressions
within the constraints. The evaluation semantics of abstract constraints
are also given in Figure \ref{fig-peq}.

@@

\begin{proof}
  If $w',\cid'$ are fresh or chosen the result is
  trivial.  Otherwise, it must be the case that at least two
  distinct variables $x_1$ and $x_2$ in $\eqs$ are renamed as a single
  variable $x$ in $\eqs'$, given freshness of $w,\cid$. Let
  $\mathit{rename}$ be the function that maps variables in $\eqs$ to
  variables in $\eqs'$ such that $\mathit{rename}(\eqs) = \eqs'$. Assume
  $\store' \models \eqs'$, and define $\store$ such that:
  $$
  \forall x \in \dom(\vars(E)) . \store(x) \defeq \store'(\mathit{rename}(x)) 
  $$
  Then $\store$ must be a model of $\eqs$, which is a contradiction. 
\end{proof}

@@

The \TirName{HardPack} rule uses \TirName{GenEntails} to ensure that
the annotated pre and postconditions are correct for a given function,
if they are defined. It is in fact not necessary for \emph{any} pre
and postconditions to be defined, but their intent is to enable
fine-tuning of postconditions for improving verification efficiency as
discussed above and later in Section \ref{section-examples}.  While
not relevant to the theory, an important implementation detail is that
verification of any given function $f$ only needs to be performed
once, and can then be memoized for other applications using
the $\TirName{App}$ rule as a consequence of Lemma \ref{lemma-genentails}
(and more precisely of Corollary \ref{cor-metahtrip}).

@@

    \peq_2 \redx \eqs_2^1 \wedge \eqs_2^2
  \end{mathpar}
  and by inversion of the $\TirName{Seq}$ rule we have:
  \begin{mathpar}
    \htrip{\peq_1^1}{\cmd_1}{\peq_2^1}

    \htrip{\peq_1^2}{\cmd_2}{\peq_2^2}
  \end{mathpar}
  and by the induction hypothesis we have:
  \begin{mathpar}
    \htrip{\eqs_1^1}{\cmd_1}{\eqs_2^1}

    \htrip{\eqs_1^2}{\cmd_2}{\eqs_2^2}
  \end{mathpar}
  But by \TirName{Hyp} we have:
  $\htrip{\eqs_1^1 \wedge (\eqs_2^1 \impl \eqs_1^2)}{\cmd_1}{\eqs_2^1 \wedge \eqs_1^2}$
  and by sanity conditions we have
  $\vars(\eqs_2^1) \cap \avars(\prog_2) = \varnothing$ so by \TirName{Frame} we
  have
  $\htrip{\eqs_2^1 \wedge \eqs_1^2}{\cmd_2}{\eqs_2^1 \wedge \eqs_2^2}$.
  Thus by $\TirName{Seq}$ we have:
  $$\htrip{\eqs_1^1 \wedge (\eqs_2^1 \impl \eqs_1^2)}{\prog_1;\prog_2}{\eqs_2^1 \wedge \eqs_2^2}$$

@@

\begin{corollary}
  \label{cor-mainhtrip}
  If $\htrip{\peq_1}{\ttt{main()}}{\peq_2}$ and $\ttt{main}() \redx \prog$ and
  $\peq_1 \redx \eqs_1$ and $\peq_2 \redx \eqs_2$ then
  $\htrip{\eqs_1}{\prog}{\eqs_2}$.
\end{corollary}

>>>>

The $\metaprot$ language \cite{skalka-near-ppdp24} includes structured
data and function definitions for defining composable protocol
elements at a higher level of abstraction than $\minicat$.  The
$\metaprot$ language is a \emph{metalanguage} aka metaprogramming
language, where an $\fedprot$ protocol is the result of
computation. In addition to these declarative benefits of $\metaprot$,
component definitions support compositional verification of larger
protocols. This includes an automated verification of algebraic
program properties expressed as Hoare logic assertions that we
introduce in this Section. Furthermore, we can compositionally verify
confidentiality and integrity properties expressed as types, as we
will discuss in Sections \ref{section-metaty} and especially
\ref{section-examples} where we present and discuss
extended examples of $\metaprot$ programs.

@@

The syntax of $\metaprot$ is defined in Figure
\ref{fig-metaprotsyntax}.  It includes a syntax of values $\mv$ that
include client ids $\cid$, identifier strings $w$, expressions $\be$
in field $\mathbb{F}_p$, record values, and $\minicat$ variables
$x$. $\metaprot$ \emph{expression} forms allow dynamic construction of these
values. Note in particular that $\concat$ is string concatentation.
$\metaprot$ \emph{instructions} allow dynamic
construction of $\minicat$ protocols $\prog$ that incorporate expression
evaluation. The syntax also supports definitions of functions that
compute values $\mv$ and, as a distinct form, functions that compute
protocols $\prog$.  The latter requires type annotations on arguments
which are restricted to being either strings, client ids, or
records-- we use this type information to support Hoare logic
automation as we discuss below in Section \ref{section-metahtrip}.

Formally, we consider a complete metaprogram to include
both a codebase and a ``main'' program that uses the codebase.
For all function (expression or instruction forms) we disallow
recursion which is important guarantee decidability
of type dependence (Section \ref{section-metaty}).
\begin{definition}
A \emph{codebase} $\codebase$ is a list of function 
declarations. We write $ \codebase(f) = y_1,\ldots,y_n,\ e$
if $f(y_1,\ldots,y_n) \{ e \} \in \codebase$, and we
write  $ \codebase(f) = y_1 : \tau_1, \ldots, y_n : \tau_n, \instr$
if $f(y_1 : \tau_1, \ldots, y_n : \tau_n) \{ \instr \} \in \codebase$.
%A \emph{metaprogram}, aka \emph{metaprotocol}  is a pair of a 
%codebase and expression $\codebase, e$. We may omit
%$\codebase$ if it is clear from context.  
\end{definition}

@@

%Note that we do not include an evaluation
%rule for the form $\eqcast{\mx{e}{e}}{e}$ which is a type
%annotation that we assume is erased from programs prior to
%evaluation. We defer discussion of this form to Section
%\ref{section-sharety}

@@

$\metaprot$ instruction functions can optionally be annotated with pre
and postconditions. To model this in our theory we posit functions
$\precond$ and $\postcond$ that specify conditions for instruction
functions $f \in \dom(\codebase)$.  Note that $\precond(f)$ or
$\precond(f)$ may be undefined if no annotation is given for $f$. In
actual code, we write pre and postconditions directly before and after
functions to define them. Here is a simple example function
$\ttt{bar}$ with pre and postcondition annotations. Note that the
annotations are abstract with respect to the input string $\ttt{x}$,
and that string concatenation can be used in pre and postcondition
constraints:
\begin{verbatimtab}
precondition: ( m[x++"foo"]@1 == 3 )
bar(x:string){ m[x++"bar"]@2 := (m[x++"foo"] + m[x++"baz"])@1 }
postcondition: ( [m[z++"bar"]@2 == m[x++"baz"]@1 + 3 )
\end{verbatimtab}
Since expressions can occur in $\metaprot$ constraints, they are not
SMT constraints, but abstractions of constraints parameterized by
the formal parameters of the function they annotate. We denote these
\emph{abstract constraints} as $\peq$ with the syntax given
in Figure \ref{fig-peq}. When the function is applied, the pre and postconditions
are instantiated as SMT constraints, via evaluating the expressions
within the constraints. The evaluation semantics of abstract constraints
are also given in Figure \ref{fig-peq}.

@@

\begin{proof}
  If $w',\cid'$ are fresh or chosen the result is
  trivial.  Otherwise, it must be the case that at least two
  distinct variables $x_1$ and $x_2$ in $\eqs$ are renamed as a single
  variable $x$ in $\eqs'$, given freshness of $w,\cid$. Let
  $\mathit{rename}$ be the function that maps variables in $\eqs$ to
  variables in $\eqs'$ such that $\mathit{rename}(\eqs) = \eqs'$. Suppose
  on the contrary that 
  $\store' \models \eqs'$ and $\store' \not\models \eqs$, and define $\store$ such that:
  $$
  \forall x \in \dom(\vars(E)) . \store(x) \defeq \store'(\mathit{rename}(x)) 
  $$
  Then $\store$ must be a model of $\eqs$, which is a contradiction. 
\end{proof}

@@

The \TirName{HardPack} rule uses \TirName{GenEntails} to ensure that
the annotated pre and postconditions are correct for a given function,
if they are defined. It is in fact not necessary for \emph{any} pre
and postconditions to be defined, since the analysis will infer valid
pre and postconditions in their absence by rule \TirName{Fn}, but
their intent is to enable fine-tuning of pre and postconditions for
improving verification efficiency as discussed above and later in
Section \ref{section-examples}.  An important implementation detail is
that verification of any given function $f$ only needs to be performed
once, and can then be memoized for other applications using the
\TirName{App} rule as a consequence of Lemma \ref{lemma-genentails}
(and more precisely of Corollary \ref{cor-metahtrip}).

@@

    \peq_2 \redx \eqs_2^1 \wedge \eqs_2^2
  \end{mathpar}
  and by inversion of the $\TirName{Seq}$ rule we have $\htrip{\peq_1^1}{\cmd_1}{\peq_2^1}$ and $\htrip{\peq_1^2}{\cmd_2}{\peq_2^2}$,
  %\begin{mathpar}
  %  \htrip{\peq_1^1}{\cmd_1}{\peq_2^1}
  %
  %  \htrip{\peq_1^2}{\cmd_2}{\peq_2^2}
  %\end{mathpar}
  and by the induction hypothesis we have $\htrip{\eqs_1^1}{\cmd_1}{\eqs_2^1}$ and $\htrip{\eqs_1^2}{\cmd_2}{\eqs_2^2}$.
  %\begin{mathpar}
  %  \htrip{\eqs_1^1}{\cmd_1}{\eqs_2^1}
  %
  %  \htrip{\eqs_1^2}{\cmd_2}{\eqs_2^2}
  %\end{mathpar}
  But by \TirName{Hyp} we have:
  $\htrip{\eqs_1^1 \wedge (\eqs_2^1 \impl \eqs_1^2)}{\cmd_1}{\eqs_2^1 \wedge \eqs_1^2}$
  and by sanity conditions we have
  $\vars(\eqs_2^1) \cap \avars(\prog_2) = \varnothing$ so by \TirName{Frame} we
  have
  $\htrip{\eqs_2^1 \wedge \eqs_1^2}{\cmd_2}{\eqs_2^1 \wedge \eqs_2^2}$.
  Thus by $\TirName{Seq}$ we have:
  $$\htrip{\eqs_1^1 \wedge (\eqs_2^1 \impl \eqs_1^2)}{\prog_1;\prog_2}{\eqs_2^1 \wedge \eqs_2^2}$$

@@

\begin{corollary}
  \label{cor-mainhtrip}
  If $\htrip{\peq_1}{\ttt{main()}}{\peq_2}$ and $\ttt{main}() \redx \prog$ and
  $\peq_1 \redx \eqs_1$ and $\peq_2 \redx \eqs_2$ then
  $\htrip{\eqs_1}{\prog}{\eqs_2}$ is valid.
\end{corollary}

### 2025-11-24 toplas26/metaty.tex
attempt at intro
checkpoint

\section{$\metaprot$ Type Checking}

@@

A fundamental component of the system is automated share type checking
of noninteractive computations.  We define an algorithmic, syntax
directed subset of noninteractive share typing as follows:
\begin{definition}
  Define $\Gamma \Vdash \stt : \sty$ iff $\Gamma,\true \Vdash \stt : \sty$ without the
  use of \TirName{ShareEntails} and \TirName{PubEntails}.
\end{definition}

@@

The syntax of type annotations $\sta$ is defined in Figure
\ref{fig-sta}, which we extend the language of commands $\cmd$ to
include. Type annotations are of the form $e_1 \kwas e_2$, which
defines an SMT equivalence, and $e : \sty$ which are verified using
the automated $\Vdash$ typing judgement-- the key idea here being that
explicit equivalences can stand in for implicit \TirName{ShareEntails}
and \TirName{PubEntails} judgements. In the semantics type annotations
are interpreted as no-ops, and their integration in Hoare triple
derivations requires annotated equivalences to be included in
preconditions.  In an implementation, Hoare triple verification can be
conducted independently prior to type checking.

@@

Programmers can also specify bindings for local computations, for
example if $\mx{x}{1},\mx{x}{2}$ are shares obtained by, e.g., local
homomorphic addition, the programmer can specify
$[\mx{x}{1},\mx{x}{2}] : \sharety$. This supports compositionality of
type checking. Thus, in the rules for share type annotations of the
form $\notg{\stt} : \sty$, we have different rules for checking local and interactive
$\sharety$ type ascriptions (\TirName{LocalShares} and \TirName{GenShares},
respectively), and for checking local and interactive
$\pubty$ type ascriptions (\TirName{LocalPublic} and \TirName{MaskedPublic},
respectively). In these rules we use of definitions $\xdefs$ to refer to
SMT equivalences, and $\Vdash$ to verify share typing.

@@

Rules for other commands are defined in Figure \ref{fig-shtripcmd}.
As anticipated above, the \TirName{Defn} rule automatically adds the
protocol definition of variables to $\xdefs$ as a default equivalence,
which may allow automatic share typing without any use of
\TirName{Coerce}. The most complex rules are for function application
and definition (\TirName{App} and \TirName{Fn}). These rules allow for
generalization and instantiation of share type environments and
thus compositionality in typing. Generalized, aka abstract
share type environments are dependent on $\stringty$ and
$\cidty$ types, and we equate them up to evaluation in
our rules.
\begin{definition}[Abstract Share Type Environments]
  We write $\notg{\Gamma}$ to denote sets of bindings $\notg{\stt} : \sty$, and
  $\notg{R}$ to denote sets of expressions (that evaluate to random variables).
  We define evaluation of these, respectively, as follows:
  \begin{mathpar}
  \inferrule
      {\notg{\stt}_1 \redx \stt_1\ \cdots\ \notg{\stt}_n \redx \stt_n}
      {\setit{\notg{\stt}_1 : \sty_1, \ldots, \notg{\stt}_n : \sty_n} \redx
        \setit{\stt_1 : \sty_1, \ldots, \stt_n : \sty_n}}

  \inferrule
      {e_1 \redx \rx{w_1}{\cid_1}\ \cdots\ e_1 \redx \rx{w_n}{\cid_n}}
      {\setit{e_1,\ldots,e_n} \redx
        \setit{\rx{w_1}{\cid_1}, \ldots, \rx{w_n}{\cid_n}}}
  \end{mathpar}
\end{definition}

We also introduce dependent $\Pi$ types for functions, that allow
dependence on $\stringty$ and $\cidty$ types.
\begin{definition}[$\metaprot$ Function Types]
  Dependent function types are of the syntactic form
  $\Pi y_1,\ldots,y_n. \notg{\Gamma} \rightarrow (\notg{\Gamma}, \notg{R})$.
  where $y_1,\ldots,y_n$ range over $\stringty$ or $\cidty$ types.
\end{definition}
As defined in \TirName{Fn}, a dependent function type $\Pi
y_1,\ldots,y_n. \notg{\Gamma_1} \rightarrow (\notg{\Gamma_2},
\notg{R})$ specifies that, given share typing assumptions in
$\notg{\Gamma_1}$, application the function results in the bindings in
$\notg{\Gamma_2}$ by using the random values in $\notg{R}$. It is
always the case that the type is closed, i.e., only $y_1,\ldots,y_n$
can occur free in $\notg{\Gamma_1}$, $\notg{\Gamma_2}$ $\notg{R}$.
Type checking for functions is accomplished by using fresh ``witness''
values of $\stringty$ and $\cidty$ types to instantiate dependent
variables, similarly to the \TirName{GenEntails} rule. As defined in
the \TirName{App} rule, typing ensures that application of the
function instantiates the dependencies, checks that the instantiation
of $\notg{\Gamma_1}$ is contained in the share typing environment, and
adds the instantiation of $\notg{\Gamma_2}$ as an effect, as will as
the instantiation of $\notg{R}$ with linearity enforced. A practical
programming detail is where the share type environment precondition
$\notg{\Gamma_1}$ is defined.  In our implementation, we write these
as an additional component of \ttt{precondition} annotations, as
illustrated in extended examples discussed in Section
\ref{section-examples}.

>>>>

\section{$\metaprot$ Type Checking}
\label{sec:metapr-type-check}

@@

A fundamental component of the system is automated share type checking
of noninteractive computations.  We define an algorithmic, syntax
directed subset of noninteractive share typing as follows:
\begin{definition}
  Define $\Gamma \Vdash \stt : \sty$ iff $\Gamma,\true \vdash \stt : \sty$ without the
  use of \TirName{ShareEntails} and \TirName{PubEntails}.
\end{definition}

@@

The syntax of type annotations $\sta$ is defined in Figure
\ref{fig-sta}, which we extend the language of commands $\cmd$ to
include. Type annotations are of the form $e_1 \kwas e_2$, which
defines an SMT equivalence-- the key idea here being that explicit
equivalences can stand in for implicit \TirName{ShareEntails} and
\TirName{PubEntails} judgements-- and $\notg{\stt} : \sty$ which
defines a share type assertion verified using the automated $\Vdash$
typing judgement. In the $\metaprot$ semantics type annotations are
interpreted as $\pskip$s, while their integration in Hoare triple
derivations requires annotated equivalences to be included in
preconditions.  In an implementation, Hoare triple verification can be
conducted independently prior to type checking.

@@

Programmers can also specify bindings for local computations, for
example if $\mx{x}{1},\mx{x}{2}$ are shares obtained by, e.g., local
homomorphic addition, the programmer can specify
$[\mx{x}{1},\mx{x}{2}] : \sharety$. This supports compositionality of
type checking. Thus, in the rules for share type annotations of the
form $\notg{\stt} : \sty$, we have different rules for checking local and interactive
$\sharety$ type ascriptions (\TirName{LocalShares} and \TirName{GenShares},
respectively), and for checking local and interactive
$\pubty$ type ascriptions (\TirName{LocalPublic} and \TirName{MaskedPublic},
respectively). In these rules we use $\xdefs$ to recover defined
SMT equivalences, and $\Vdash$ to verify share typing.

@@

Rules for other commands are defined in Figure \ref{fig-shtripcmd}.
As anticipated above, the \TirName{Defn} rule automatically adds the
protocol definition of variables to $\xdefs$ as a default equivalence,
which may allow automatic share typing without any use of
\TirName{Coerce}. The most complex rules are for function application
and definition (\TirName{App} and \TirName{Fn}). These rules allow for
generalization and instantiation of share type environments and
thus compositionality in typing. Generalized aka abstract
share type environments are dependent on $\stringty$ and
$\cidty$ types, and we equate them up to evaluation in
our rules.
\begin{definition}[Abstract Share Type Environments]
  We write $\notg{\Gamma}$ to denote sets of bindings $\notg{\stt} : \sty$, and
  $\notg{R}$ to denote sets of expressions (that evaluate to random variables).
  We define evaluation of these, respectively, as follows:
  \begin{mathpar}
  \inferrule
      {\notg{\stt}_1 \redx \stt_1\ \cdots\ \notg{\stt}_n \redx \stt_n}
      {\setit{\notg{\stt}_1 : \sty_1, \ldots, \notg{\stt}_n : \sty_n} \redx
        \setit{\stt_1 : \sty_1, \ldots, \stt_n : \sty_n}}

  \inferrule
      {e_1 \redx \rx{w_1}{\cid_1}\ \cdots\ e_1 \redx \rx{w_n}{\cid_n}}
      {\setit{e_1,\ldots,e_n} \redx
        \setit{\rx{w_1}{\cid_1}, \ldots, \rx{w_n}{\cid_n}}}
  \end{mathpar}
\end{definition}
\noindent We also introduce dependent $\Pi$ types for functions, that allow
dependence on $\stringty$ and $\cidty$ types.
\begin{definition}[$\metaprot$ Function Types]
  Dependent function types are of the syntactic form
  $\Pi y_1,\ldots,y_n. \notg{\Gamma} \rightarrow (\notg{\Gamma}, \notg{R})$.
  where $y_1,\ldots,y_n$ range over $\stringty$ or $\cidty$ types.
\end{definition}
As defined in \TirName{Fn}, a dependent function type $\Pi
y_1,\ldots,y_n. \notg{\Gamma_1} \rightarrow (\notg{\Gamma_2},
\notg{R})$ specifies that, given share typing assumptions in
$\notg{\Gamma_1}$, application the function results in the bindings in
$\notg{\Gamma_2}$ by using the random values in $\notg{R}$. It is
always the case that the type is closed, i.e., only $y_1,\ldots,y_n$
can occur free in $\notg{\Gamma_1}$, $\notg{\Gamma_2}$ $\notg{R}$.
Type checking for functions is accomplished by using fresh ``witness''
values of $\stringty$ and $\cidty$ types to instantiate dependent
variables, similarly to the \TirName{GenEntails} rule. As defined in
the \TirName{App} rule, typing ensures that application of the
function instantiates the dependencies, checks that the instantiation
of $\notg{\Gamma_1}$ is contained in the share typing environment, and
adds the instantiation of $\notg{\Gamma_2}$ as an effect, as will as
the instantiation of $\notg{R}$ with linearity enforced. A practical
programming detail is where the share type environment precondition
$\notg{\Gamma_1}$ is defined.  In our implementation, we write these
as an additional component of \ttt{precondition} annotations, as
illustrated in extended examples discussed in Section
\ref{section-examples}.
